TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-11 ISORC2017/paper.tex
Adjustment

The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices, smart devices, and smart homes, will be connected via the Internet to further enrich people's lives.
However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of, for example, low memory capacity.

@@

This paper proposes a component-based TCP/IP protocol stack for embedded systems--TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS)--to improve the configurability and scalability of TCP/IP software.
Because it is a component system suitable for embedded systems, TECS \cite{par:TECS} \cite{par:hr-tecs} is used to componentize TINET in the proposed protocol stack.
As TECS supports static configurations that statically define component behaviors and interconnections, it can optimize the componentization overhead.

In addition to satisfying the original TINET specifications, the proposed framework utilizes the TECS dynamic connection capability to dynamically switch component bindings.
Although general TCP/IP protocol servers dynamically process requested ports, i.e., Hypertext Transfer Protocol (HTTP, port: 80) and Hypertext Transfer Protocol Secure (HTTPS, port: 443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
TINET supports the static generation of Communication Endpoints (CEPs) and Reception Points (REPs), which are similar to sockets.
As TINET+TECS, like TINET, statically generates components and dynamically combines them in the same manner, TINET+TECS reduces the dynamic increase of memory consumption.

@@

This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities in order to improve configurability with small overheads.
Furthermore, the advantages of dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.

{\bf Contributions:} This paper provides the following contributions:

\begin{enumerate}

    \item {\bf Improve configurability}\mbox{}\\
        Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
        In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.

    \item {\bf Dynamic connection method}\mbox{}\\
        Dynamically switching the binding of components, that is, switching between a TINET communication endpoint and REP, realizes a TCP/IP protocol stack for an embedded system.

    \item {\bf Support legacy codes}\mbox{}\\
        TINET+TECS can be applied to existing applications because TECS supports the ability of the adapter to call TECS functions from C codes. 
    % \item {\bf Software visualization}

\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and its basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates its advantages.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model of TINET+TECS}
    \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component diagram}
    \label{fig:ComponentDiagram}
\end{figure}

@@

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions that defines the interface definition of the {\it cell}.
The {\it cell's} {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

@@

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s''--for instance, sIPv4Output (Fig. \ref{src:signature}).
        To clarify the function of an interface, specifiers such as [in], [out], and [inout] are used in TECS to represent the input, output, and input/output, respectively.
        Similarly, [size\_is({\it len})] represents an array of size {\it len}.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description}
\label{src:signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines the {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;

    /* Call port */
    call sEthernetOutput cEthernetOutput;
    /* Omit: other call ports */

    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\caption{Celltype description}
\label{src:celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig. \ref{src:build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
        {\it C\_EXP} can be used to call macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tIPv4Output IPv4Output {
    /* Omit: other build description */

    fragInit = 0; /* Attribute */
};
cell tTCPOutput TCPOutput {
    cIPv4Output = IPv4Output.eOutput;
    /* Omit: other build description */
};
\end{lstlisting}
\caption{Build description}
\label{src:build}
\end{figure}

\end{description}

@@

The components of a TINET+TECS protocol stack are shown in Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
By using such small grain components, software visibility is improved.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of a protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

The components of each protocol are described in the following.\\

@@

{\bf Network layer:}
tIPv4Input and tIPv4Output are components that perform, respectively, the receiving and sending processing in the network layer.
The tIPv4Functions component performs functions such as checksum, the tICMP component is for implementing the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.

{\bf Data link layer:}
tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components for performing, respectively, receiving and sending processing in the data link layer.
The tArp component is used for the Address Resolution Protocol (ARP).

{\bf Physical layer:}
The tNetworkInterfaceContoroller component implements a network device driver.
Software can be run on other devices by replacing the component because only the component depends on the target device.\\

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

@@

TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connectivity, a selector should be defined.
A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
The cREP ports form a call port array connecting to connecting to all tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 13--15 in Fig. \ref{src:DynamicCDLcode}).
The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};

celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};

celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\caption{Signature and celltype description for dynamic connection}
\label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\caption{Accept function (Dynamic connection example)}
\label{src:DynamicCcode}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS adapter}
    \label{fig:TECS_Adapter}
\end{figure}

@@

GR-PEACH was employed as the evaluation board.
Detailed specifications of the board are shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2
To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data transmission and reception.

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

@@

To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the comparison results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \caption{Execution times of TINET and TINET+TECS}
    \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{table}[t]
    \centering
    \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

As shown in TABLE \ref{tab:EvaluationOfConfigurabilty}, the code lines for modification were measured to demonstrate the improved configurability.
This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.

\begin{table}[t]
    \centering
    \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (- Default)  & CDL  \\ \hline
        Default          &   325.23 KB  &             0 KB    &  0 lines   \\
        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for two cases (without/with dynamic connection)}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
    \caption{Memory consumption in two cases (with/without dynamic connection)}
    \label{fig:EvaluationOfDynamicConnection}
\end{figure}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

>>>>

The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of low memory capacity.

@@

This paper proposes a component-based TCP/IP protocol stack for embedded systems--TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS)--to improve the configurability and scalability of TCP/IP software.
Because it is a component system suitable for embedded systems, TECS is used to componentize TINET in the proposed protocol stack.
As TECS supports static configurations that statically define component behaviors and interconnections, it can optimize the componentization overhead.

To satisfy the original TINET specifications, TINET+TECS utilizes the TECS dynamic connection method to dynamically switch component bindings.
Although general TCP/IP protocol servers dynamically process requested ports, i.e., Hypertext Transfer Protocol (HTTP, port:80) and Hypertext Transfer Protocol Secure (HTTPS, port:443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
TINET supports the static generation of Communication Endpoints (CEPs) and Reception Points (REPs), which are similar to sockets.
As TINET+TECS, like TINET, statically generates components and dynamically combines them in the same manner, TINET+TECS reduces the dynamic increase of memory consumption.

@@

This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities to improve configurability with small overheads.
Furthermore, the advantages of dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.

% {\bf Contributions:}
This paper provides the following contributions:

{\bf Improve configurability:}
Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.

{\bf Dynamic connection method:}
Dynamically switching the binding of components, that is, switching between a TINET communication endpoint and REP, realizes a TCP/IP protocol stack for an embedded system.

{\bf Support legacy codes:}
TINET+TECS can be applied to existing applications because TECS supports the ability of the adapter to call TECS functions from C codes. 
% \item {\bf Software visualization}

% {\bf Organization:}
The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and its basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates its advantages.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
    \vspace{-1mm} \caption{System model of TINET+TECS}
    \vspace{-1mm} \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-1mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
    \vspace{-1mm} \caption{Component diagram}
    \vspace{-1mm} \label{fig:ComponentDiagram}
\end{figure}

@@

The type of {\it entry}/{\it call} port is defined by a {\it signature}, a set of functions that defines the interface definition of the {\it cell}.
The {\it cell's} {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.

@@

{\bf Signature Description:}
The {\it signature} defines a {\it cell} interface.
The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s''--for instance, sIPv4Output (Fig. \ref{src:signature}).
To clarify the function of an interface, specifiers such as [in], [out], and [inout] are used in TECS to represent the input, output, and input/output, respectively.
Similarly, [size\_is({\it len})] represents an array of size {\it len}.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description}
\vspace{-1mm} \label{src:signature}
\end{figure}

{\bf Celltype Description:}
The {\it celltype} defines the {\it entry} ports, {\it call} ports, attributes, and variables.
A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
{\it Call} ports are defined similarly.
Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;
    /* Call port */
    call sEthernetOutput cEthernetOutput;
    /* Omit: other call ports */
    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\vspace{-1mm} \caption{Celltype description}
\vspace{-1mm} \label{src:celltype}
\end{figure}

{\bf Build Description:}
The build description is used to instantiate and bind {\it cell}s.
Fig. \ref{src:build} shows an example of a build description.
A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
% A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
{\it C\_EXP} can be used to call macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tIPv4Output IPv4Output {
    /* Omit: other build description */
    fragInit = 0; /* Attribute */
};
cell tTCPOutput TCPOutput {
    cIPv4Output = IPv4Output.eOutput;
    /* Omit: other build description */
};
\end{lstlisting}
\vspace{-1mm} \caption{Build description}
\vspace{-1mm} \label{src:build}
\end{figure}

@@

The components of a TINET+TECS protocol stack are shown in Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
By using such small grain components, software visibility is improved.
The components of each protocol are described in the following.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \vspace{-1mm} \caption{Component diagram of a protocol stack}
    \vspace{-1mm} \label{fig:ComponentProtocolStack}
\end{figure}

@@

{\bf Network layer:}
The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
The tIPv4Functions component performs functions such as checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.

{\bf Data link layer:}
tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components for performing, respectively, receiving and sending processing in the data link layer.
The tArp component is for implementing the Address Resolution Protocol (ARP).

{\bf Physical layer:}
The tNetworkInterfaceContoroller component implements a network device driver.
Software can be run on other devices by replacing the component because only the component depends on the target device.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
    \vspace{-1mm} \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
    \vspace{-1mm} \caption{Differences between in/out and send/receive}
    \vspace{-1mm} \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-1mm} \label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-1mm} \caption{Dynamic connection}
    \vspace{-1mm} \label{fig:DynamicConnection}
\end{figure}

@@

TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
    \vspace{-1mm} \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connectivity, a selector should be defined.
A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig. \ref{src:DynamicCDLcode}).
The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature and celltype description for dynamic connection}
\vspace{-1mm} \label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\vspace{-1mm} \caption{Accept function (Dynamic connection example)}
\vspace{-1mm} \label{src:DynamicCcode}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
    \vspace{-1mm} \caption{TECS adapter}
    \vspace{-1mm} \label{fig:TECS_Adapter}
\end{figure}

@@

GR-PEACH was employed as the evaluation board.
Detailed specifications of the board are shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

@@

To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
    \vspace{-1mm} \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

As shown in TABLE \ref{tab:EvaluationOfConfigurability}, the code lines for modification were measured to demonstrate the improved configurability.
This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (-- Default) & CDL  \\ \hline
        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection cases}
    \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}
